%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape AMAN HOGAN-BAILEY} \\ \vspace{3pt}
    2026 Kings Forest Drive, Forney, TX 75126 \\ \vspace{3pt}
    \small \raisebox{-0.1\height}\faPhone\ 214-900-7302 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {aman.hogan-bailey@mavs.uta.edu}} ~ 
    \href{https://www.linkedin.com/in/aman-hogan-bailey/}{\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/aman-hogan-bailey}}  ~
    \href{https://github.com/AmanHogan}{\raisebox{-0.2\height}\faGithub\ {github.com/AmanHogan}}
    \vspace{3pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Arlington}{2020 -- 2023}
      {Bachelor of Science in Computer Science}{GPA: 3.8/4.0}
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small
        {
            \item
            {
                    \textbf{Languages}{: Assembly (ARM), C/C++, C\#, HTML, Java, JavaScript, LaTeX, MATLAB, .NET, Python, SQL, XML} \\
                        \vspace{2pt}
                    \textbf{Operating Systems}{: Linux, Pi OS, Ubuntu, VxWorks, Windows} \\
                                        \vspace{2pt}
                    \textbf{Software/Developer Tools}{: Android Studio, Collaborator, Docker, Eclipse, Git/Gitlab, Jira, MS Office, NetBeans, \\ Postman, Putty, Telnet, Tera Term, Unreal Engine, Visual Studio, WinSCP, Wireshark} \\
\vspace{3pt}
                    \textbf{Relevant Coursework}{: Data Structures, Agile Methodologies, Object Oriented Design, Database Systems, \\ Algorithms Analysis, Network Systems, Functional Programming} \\ 
                    \vspace{2pt}
            }
        }
    \end{itemize}    

\vspace{-15pt}

%-----------EXPERIENCE-----------
\section{Experience}

  \resumeSubHeadingListStart

    \resumeSubheading
    {Software Engineer Intern}{Richardson, TX}
    {Leonardo DRS}{June 2022 -- August 2022}
      \resumeItemListStart
        \resumeItem{Developed a collection of robust programs in VxWorks for embedded systems and RTOS and troubleshot for the optimal file transfer method.}
        \resumeItem{Configured a bootable VxWorks image to load from a USB and successfully launched it from a target board.}
        \resumeItem{Modified, debugged, and heavily documented existing code to improve maintainability, readability, and flexibility.}
      \resumeItemListEnd

    \resumeSubheading
    {Electrical Engineering Research Assistant}{Arlington, TX}
      {University of Texas at Arlington}{Feb 2022 -- May 2022}
      \resumeItemListStart
        \resumeItem{ Assist in the additional research and data collection of arc- flashes 
using DC systems with lithium-ion batteries.}
        \resumeItem{Analyze mathematical models from published papers that predict the incident 
energies of arc-flashes to derive the appropriate real-world applications.}

  \resumeItem{Verified the accuracy of experimental data to highlight any inconsistencies with previous models and experiments.
}
      
    \resumeItemListEnd

     \resumeSubheading
    {College of Engineering Co-Instructor}{Arlington, TX}
      {University of Texas at Arlington}{August 2021 -- December 2021}
      \resumeItemListStart
        \resumeItem{Taught a semester comprised of over 30+ students on how to achieve academic 
success in the college of engineering.
}
        \resumeItem{Rigorously graded assignments and projects, providing actionable feedback to help
students attain success in college.
}
  \resumeItem{Prepared robust, comprehensive lesson plans for the class while providing regular, 
additional 1:1 academic coaching to students.
}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart


      \resumeProjectHeading
        {\textbf{FAT32 Disk Image Reader} $|$ \emph{C}}{March 2022}
                    \resumeItemListStart
                        \resumeItem{Implemented logical block addressing to bypass volume ID, reserved sectors, FAT1 and FAT2, to access the clusters within a FAT32 image file.}
                        \resumeItem{Implemented a bash shell interface to traverse, delete, and copy files and directories in a FAT32 disk image.}
                    \resumeItemListEnd
                      \vspace{-13pt}

                           \resumeProjectHeading
        {\textbf{Multi-threading of Mandelbrot Fractal } $|$ \emph{C}}{February 2022}
            \resumeItemListStart
                \resumeItem{Implemented escape time algorithm to calculate the colors in the bitmap of the Mandelbrot set.}
                \resumeItem{Utilized parallelism and multi-threading to generate bitmaps of the Mandelbrot fractal, increasing the time efficiency. }
          \resumeItemListEnd 
                      \vspace{-13pt}

    
      \resumeProjectHeading
          {\textbf{On-Demand Home Service App} $|$ \emph{Java, XML}}{January 2022}
            \resumeItemListStart
                \resumeItem{Improved the app entry point speed by 80\% by streamlining the activity logic in the platform's application model.}
                \resumeItem{Designed and developed the UI, event and adapter logic, and local database functionality.}
            \resumeItemListEnd
            \vspace{-13pt}
                            \resumeProjectHeading
        {\textbf{3D Platformer } $|$ \emph{UE4, Visual Blueprint Scripting, C++}}{May 2021}
                    \resumeItemListStart
                        \resumeItem{Developed a procedurally generated textured terrain through linear interpolation and heightmap manipulation.}
                        \resumeItem{Designed original assets, layouts, and animations and applied spawn, collision, and item logic to them through C++ and visual blueprint scripting.}
                    \resumeItemListEnd
                      \vspace{-13pt}

          
    \resumeSubHeadingListEnd
\vspace{-15pt}
%

\end{document}
